Semantic Preserving Bijective Mappings for Expressions involving Special Functions between Computer Algebra Systems and Document Preparation Systems

### 2018-12-03 ReviewerResponse.txt

In the following, we respond specifically to the reviewers' comments.

@@

We explained how a power after a macro is handled in more detail and why 
optional parameters need to be handled differently than other arguments.

We gave further detailed descriptions concerning the PoM-Tagger, namely its 
parsing process and lexicon files.

We added LaTeXML to the related work section and gave a brief 
explanation with cited research (Schubotz et al., 2018, now included 
in our references), in order to explain why we did not choose MathML 
as an intermediate data format for performing translations. In that 
citation, we described detailed testing that we performed using LaTeXML 
and other state-of-the-art LaTeX to MathML conversion tools. In that
reference, we discovered several critical problems which could occur 
when translations would be performed using MathML as an intermediate data format.

Note that we did not add further comparisons with LaTeXML to our 
evaluations section, because current CAS are unable to understand MathML 
which contains special functions. Thus, in order to make a decent 
comparison, we can only compare translations without function calls or 
implement a solution which is able to overcome these problems.  Because of 
the problems which would need to be overcome, a full solution translation 
implementation using MathML is out of the scope of our current project. 
This is now all explained in detail in the new version of the manuscript.

### 2018-12-03 main.tex
Make the paper anonym again
Edit keywords and fill out article title page

\input{authors.tex}

@@

\noindent
{\it \bf Keywords:} \LaTeX, Computer Algebra System (CAS), Translation, Presentation to Computation (P2C), Special Functions

>>>>

\author{Anonymous Authors}
%\input{authors.tex}

@@

\noindent
{\it \bf Keywords:} \LaTeX, Computer Algebra System (CAS), Document Preparation System (D2P), Translation, Presentation to Computation (P2C), Special Functions
